---
title: "US Bank Integration 2.0"
output: pdf_document
documentclass: article
geometry: margin = 1.5in
bibliography: Working_Paper.bib
linkcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rmarkdown)
library(knitr)
library(xml2)
```

This is the restarting of the US bank integration project with better quality data compiled from WRDS. 


## Standard Industrial Classification Code

We include a short description of SIC codes and what they stand for. The following code scrapes the SIC code tables from the corresponding Wikipedia page. The full list can be found on the link: <http://www.ehso.com/siccodes.php>

```{r SIC_Codes_Industries}

url_SIC <- "https://en.wikipedia.org/wiki/Standard_Industrial_Classification"
webpage <- xml2::read_html(url_SIC)
SIC_tables <- rvest::html_nodes(webpage, "table")
table_1 <- rvest::html_table(SIC_tables[2], fill = F)
knitr::kable(table_1[[1]], caption = "SIC codes for industries. 
             The acronym NEC stands for 'not elsewhere classified'")  
```

As is clearly visible, the banking and finance industry is found between the SIC codes 6000 to 6799. Hence in order to collect information on banks, we need to focus on this particular subset. In the following set of codes, we display only the finance industry subgroups in the above range.

```{r SIC_Codes_Finance}
table_2 <- rvest::html_table(SIC_tables[3], fill = F)
sic_fin <- seq(6000, 6799)
table_2_fin <- table_2[[1]] %>% dplyr::filter(`SIC Code` %in% sic_fin)
knitr::kable(table_2_fin, caption = "SIC codes for finance and 
             related industry groups")
```

Further, we extract the relevant portion of the SIC table from the full list to focus on the banking and finance industry:

|SIC Code     | Industry                |
|:------------|:------------------------|
|60           |DEPOSITORY INSTITUTIONS  |
| 601         |CENTRAL RESERVE DEPOSITORY INSTITUTIONS|
|   6011      |FEDERAL RESERVE BANKS |
|   6019      |CENTRAL RESERVE DEPOSITORY INSTITUTIONS, NEC|
| 602         |COMMERCIAL BANKS |
|   6021      |NATIONAL COMMERCIAL BANKS |
|   6022      |STATE COMMERCIAL BANKS |
|   6029      |COMMERCIAL BANKS, NEC|
| 603         |SAVINGS INSTITUTIONS |
|   6035      |SAVINGS INSTITUTIONS, FEDERALLY CHARTERED|
|   6036      |SAVINGS INSTITUTIONS, NOT FEDERALLY CHARTERED|
| 606         |CREDIT UNIONS |
|   6061      |CREDIT UNIONS, FEDERALLY CHARTERED |
|   6062      |CREDIT UNIONS, NOT FEDERALLY CHARTERED |
| 608         |FOREIGN BANKING AND BRANCHES AND AGENCIES OF FOREIGN BANKS |
|   6081      |BRANCHES AND AGENCIES OF FOREIGN BANKS |
|   6082      |FOREIGN TRADE AND INTERNATIONAL BANKING INSTITUTIONS |
| 609         |FUNCTIONS RELATED TO DEPOSITORY BANKING |
|   6091      |NONDEPOSIT TRUST FACILITIES |
|   6099      |FUNCTIONS RELATED TO DEPOSITORY BANKING, NEC|
|61           |NONDEPOSITORY CREDIT INSTITUTIONS |
| 611         |FEDERAL AND FEDERALLY-SPONSORED CREDIT AGENCIES |
|   6111      |FEDERAL AND FEDERALLY-SPONSORED CREDIT AGENCIES |
| 614         |PERSONAL CREDIT INSTITUTIONS |
|   6141      |PERSONAL CREDIT INSTITUTIONS |
| 615         |BUSINESS CREDIT INSTITUTIONS |
|   6153      |SHORT-TERM BUSINESS CREDIT INSTITUTIONS, EXCEPT AGRICULTURAL |
|   6159      |MISCELLANEOUS BUSINESS CREDIT INSTITUTIONS |
| 616         |MORTGAGE BANKERS AND BROKERS |
|   6162      |MORTGAGE BANKERS AND LOAN CORRESPONDENTS |
|   6163      |LOAN BROKERS |
|67           |HOLDING AND OTHER INVESTMENT OFFICES |
| 671         |HOLDING OFFICES |
|   6712      |OFFICES OF BANK HOLDING COMPANIES |
|   6719      |OFFICES OF HOLDING COMPANIES, NEC|

We follow @Fahlenbrach_et_al:2016 in constructing our sample of US banks. We quote them (p. 6):

>We construct our sample as follows. We search the CRSP database for all firms that have an SIC code
>between 6020 and 6079 (Commercial Banks, Savings Institutions, and Credit Unions) or from 6710
>through 6712 (Offices of Bank Holding Companies) at some point in the firm’s history.

Additionally we also seek guidance from the sample construction in @Adrian_Brunnermeier:2016:

>Banks correspond to SIC codes 60, 61, and 6712; insurance companies correspond to SIC codes 63–64, 
>real estate companies correspond to SIC codes 65–6, and broker-dealers are SIC code 67 (except for
>the bank holding companies, 6712).

Since our sample and definition of the US banking system follows the discussion in @Fahlenbrach_et_al:2016 more closely, we try to construct our sample as close to theirs as we can.

## Note on CUSIPs, Tickers etc.

CUSIP, which is controlled by Standard & Poor's, is officially a 9-character string. The first 6 identify the issuer, the 7th and 8th identify the issue and the 9th is a check digit that is fully determined by the first 8 characters. CRSP (the default data source for Eventus on WRDS and, when subscribed and installed, for Eventus for Windows and Linux) omits the check digit and uses an 8-character CUSIP field. Common equity issues always have an 8th character of 0. As CRSP covers only common stocks, all CUSIPs in CRSP end in 0 as the 8th character. CUSIPs from other sources that have a non-zero digit in the 8th position are not common stock CUSIPs.

Given the above-described structure, we can see that eight characters are required to uniquely identify a security

Tickers can be reused and several companies might be listed in different exchanges with the same ticker code (<http://findb.aalto.fi/faq/database_general.html>)

### Directory Management

First we need to be able to navigate to the directory where data are stored.

```{r directory_management}

data_folder_path <- "../Data_Bank_Int/"
file_path <- paste0(data_folder_path, "SICCD_6020-6079_6710-6712_20171105.dta")
```

The relevant file here is a Stata file with extension `.dta`. There is a special reason for choosing the Stata file format instead of the usual Excel or `.csv` format preferred for doing data analysis in `R`. This is so since the file containing daily stock prices of all banks in the US is very large and its number of rows exceeds the maximum row limit in Excel, which is around 1 million. Hence if one were to download and read the data via Excel, only the first one million or so rows will be displayed and stored.[^1]

[^1]: A previous difficulty encountered in this project was that the list of banks corresponding to SIC codes between 6000-6799 did not include the G-SIBs. However, the reason for that mystery was the lack of rows from 1-2 million being displayed/stored in Excel due to its size limitation.

### Tidy Reading

After navigating to the relevant folder, one needs to be able to read the data file, stored in this case, with a `.dta` extension. 

```{r reading_data, warning = F}

data <- haven::read_dta(file_path)

bank_name <- data %>% dplyr::distinct(comnam)
```



# References