---
title: "Integration Among US Banks: Rerun"
author: Abhinav Anand and John Cotter
date: '`r format(Sys.time(), "%Y/%m/%d")`' #current date

output:
  pdf_document:
    keep_tex: true

fontsize: 11pt
documentclass: article
geometry: margin = 1.5in

linkcolor: blue
urlcolor: red
citecolor: magenta

# citation_package: natbib
# bibliography: Working_Paper.bib

header-includes:
   - \linespread{1.25}
   - \usepackage{amsmath}


---


```{r setup, eval=T, message=FALSE, warning=F, include=FALSE}

library(tidyverse)
library(rmarkdown)
library(knitr)
library(moments) 
library(broom)

knitr::opts_chunk$set(echo = F, 
                      warning = T, 
                      message = F, 
                      eval = T, 
                      include = T,
                      fig.height=5.5, 
                      fig.width=5.5,
                      fig.align = 'center'
                      )

# Preprocess, then compute then postprocess
# Includes two nested scripts 
source('Int_Banks_US_panel_estimation.R', echo = F)

# Further Tests to Do:

# 8. WHY does PCA capture integration? Improve Puk and Roll's answer.
# 9. What are the identities of the left tail outliers in the boxplots?
# 10. Correlation between quarterly integration and quarterly returns?
# 11. How do factor loadings evolve? (Brennan question)
# 12. How does CHANGE in integration behave? Distribution? Time Series? Crises?
# 13. Do clustering at the level of time also


```

# Median US Bank Integration 

```{r med_US_bank_int, fig.height= 6, fig.width=11}

plot_med_bank_int

```

## Linear Time Trends

```{r linear_trend}

knitr::kable(broom::tidy(int_dummy_recession))

```

# Empirical Distribution of US Bank Integration

```{r emp_distr_US_bank_int}

boxplot_int_yearly

```

# Most Integrated Banks

```{r most_int}

med_top_25 <- med_top_25_admissible %>%
  dplyr::rename(., "Bank" = rowname) %>%
  dplyr::rename(., "Median_Integration" = value)

knitr::kable(med_top_25)


barplot_top_25

```

# Explantory Power of Eigenvectors

```{r expl_power_eig_vec}

boxplot(t(var_share_df[1:30, ]))

barplot(expl_power_eig_med[1:30])

```

# Linear Time Trends for Bank Integration 

```{r time_trend_banks}

knitr::kable(trend_T_p_val_df)


```

# Systemic Banks' Integration

```{r systemic, fig.width=11, fig.height=6}

plot_systemic

```

# Effect of NBER Recessions on Bank Integration

```{r dummy_recession}

#knitr::kable(int_dummy_recession)

```

# Integration Variation with SIC category

```{r SIC_Categ}

# Summary stats of median bank integration for each SIC class
bank_SIC_summ_stat

# Boxplot of above
box_int_SIC_Categ

# Median bank integration plot

matplot(bank_int_SIC_med, 
        type = "l", 
        lty = 1, 
        lwd = 1, 
        col = 1:4, 
        xlab = "Quarters", 
        ylab = "Median bank Intgeration"
        )

legend(65, 0.4, 
       legend = c("Comm", "Cred_Uni", "Saving", "Holding"), 
       col = 1:4, 
       lty = 1, 
       cex=0.6
       )


```

# Differencing the Intgration Series

```{r Diff}

# GSIBs 
matplot(int_diff_sys_gsib, 
        type = "l", 
        lty = 1, 
        col = 1:ncol(int_diff_sys_gsib),
        xlab = "Quarters",
        ylab = "GSIBs Differenced Integration"
        )

legend(60, -0.4, 
       legend = name_GSIB, 
       col = 1:length(name_GSIB), 
       lty = 1, 
       cex = 0.25
       )


```


# Panel Estimation

```{r panel_est}

# Pooled
knitr::kable(panel_est_full$Pool, digits = 4, caption = "Pooled Model")

# Fixed Effects
knitr::kable(panel_est_full$Fixed, digits = 4, caption = "Fixed Effects Model")

```